\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-17 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating proof in the appendix

\subsection{Proximal Update}\label{subsec:ProxUpdate}
Looking at \eqref{NewPotentials} and \eqref{NewPDE}, it is natural to consider an energy functional of the form
\begin{align}
\Phi(\tilde{\rho}) := \!\!\displaystyle\int_{\mathbb{T}^{n}\times\mathbb{R}^{n}}\!\!\!\left(\!\bm{M}^{-1}\bm{\Gamma}U(\bm{\xi})+ F\left(\bm{\eta}\right) + \frac{1}{2}\log\tilde{\rho}\!\right)\tilde{\rho}\:\differential\bm{\xi}\:\differential\bm{\eta},
\label{LyapButNotProx}	
\end{align}
which is the sum of a potential energy (expected value of scaled $U$), a weighted kinetic energy (expected value of $F\left(\bm{\eta}\right)$), and an internal energy (scaled negative entropy, the entropy being $-\int\tilde{\rho}\log\tilde{\rho}$). Indeed, it can be shown that (Appendix \ref{AppLyap}) the functional \eqref{LyapButNotProx} is a Lyapunov functional, i.e., $\Phi$ is decreasing along the solution of \eqref{NewPDE}.

However, it is not possible

>>>>

\subsection{Proximal Update}\label{subsec:ProxUpdate}
Looking at \eqref{NewPotentials} and \eqref{NewPDE}, it is natural to consider an energy functional of the form
\begin{align}
\Phi(\tilde{\rho}) := \!\!\displaystyle\int_{\mathbb{T}^{n}\times\mathbb{R}^{n}}\!\!\!\left(\!\bm{M}^{-1}\bm{\Gamma}U(\bm{\xi})+ F\left(\bm{\eta}\right) + \frac{1}{2}\log\tilde{\rho}\!\right)\tilde{\rho}\:\differential\bm{\xi}\:\differential\bm{\eta},
\label{LyapButNotProx}	
\end{align}
which is the sum of a potential energy (expected value of scaled $U$), a weighted kinetic energy (expected value of $F\left(\bm{\eta}\right)$), and an internal energy (scaled negative entropy, the entropy being $-\int\tilde{\rho}\log\tilde{\rho}$). Indeed, it can be shown that (Appendix \ref{AppLyap}) the functional \eqref{LyapButNotProx} is a Lyapunov-like functional, i.e., $\Phi$ is decreasing along the solution of \eqref{NewPDE}.

However, unlike the gradient drift case mentioned in Sec. \ref{subsec:GenGradDescent}, it is not possible to express the right hand side of \eqref{NewPDE} as the Wasserstein gradient of the functional \eqref{LyapButNotProx}.
